%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj (https://github.com/sb2nov/resume/blob/master/sourabh_bajaj_resume.tex)
% Edited by: Dileep Nackathaya
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheadingMod}[5]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Large Dileep Nackathaya} & Email : \href{mailto:dileepbn@gmail.com}{dileepbn@gmail.com}\\
		\href{https://github.com/dnackat/}{https://github.com/dnackat/} & Mobile : +91-7899129478 \\
		\href{https://www.linkedin.com/in/dnackat/}{https://www.linkedin.com/in/dnackat/} \\
	\end{tabular*}
	
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheadingMod
	{North Carolina State University}{Raleigh, NC, USA}
	{Master of Science in Mechanical Engineering;  GPA: 3.75/4.00}{Aug 2010 -- Dec 2012}
	{Specialization: Computational Fluid Dynamics (CFD)}{}
	\resumeSubheading
	{Visveswaraya Technological University}{Belgaum, India}
	{Bachelor of Engineering in Mechanical Engineering;  Grade: First Class (74\%)}{Sep. 2006 -- July. 2010}
	\resumeSubHeadingListEnd
	
	%----------LEARNING--------------------
	\section{Continuous Learning}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Coursework (edX, Coursera, Swayam) and projects}{Udupi, India}
	{Pursued on my sabbatical from the industry  (progress documented on LinkedIn and GitHub)}{Jan 2018 -- Present}
	\resumeItemListStart
	%\resumeItem{\href{https://www.edx.org/micromasters/mitx-statistics-and-data-science/}{Statistics and Data Science MicroMasters (offered by MITx on edX)}}
	%{Four graduate level credit-eligible courses with assignments, projects, and exams in Probability, Statistics, Data Analysis, and Machine Learning \textit {\small (Skills: Python, R, PyTorch, NumPy, SciPy, Matplotlib, Scikit-learn).}}
	%\resumeItem{\href{https://www.coursera.org/learn/machine-learning/}{Machine Learning (taught by Prof. Andrew Ng on Coursera)}}
	%{An introductory machine learning course with eight programming projects (\textit{\small Skills: MATLAB/GNU Octave}).}
	\resumeItem{Thermal and Fluid Sciences, Mathematics Courses}
	{Computational Fluid Dynamics using FVM, Calculus Applied, Advanced Fluid Mechanics, Multivariable Calculus, Vector Calculus for Engineers, Linear Algebra}
	\resumeItem{CFD simuations on open-source CFD codes, CAD packages, and meshers}
	{Performed CFD simulations using OpenFOAM and code\_saturne with geometries created in FreeCAD and Salome, and meshed with native meshers, cfMesh, and gmsh.}
	\resumeItem{Stastics, Data Science, and Programming}
	{Completed certificate courses in probability theory, statistics, machine learning, and data analysis offered by MIT on edX. Other courses: Using Python for research, Introduction to Computer Science and programming using Python, Unix Workbench.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd

	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{\href{https://www.johnzinkhamworthy.com/}{John Zink Hamworthy Combustion}}{Tulsa, OK, USA}
	{Computational Fluid Dynamics Engineer, R \& D Group}{Jun 2013 -- Aug 2017}
	\resumeItemListStart
	\resumeItem{Simulation and Analysis}
	{Created CFD models of industrial burners, flares, thermal oxidizers, and vapor recovery systems and analyzed simulation data. Prepared customer reports on findings of these analyses.}
	\resumeItem{Product Development}
	{Leveraged data from CFD simulations and analyses to provide insights on designing new products and improving existing ones.}
	\resumeItem{Troubleshooting}
	{Analyzed data from customer sites and ran simulations to troubleshoot on-site product issues.}
	\resumeItem{Skills/Tools}
	{Star-CCM+; Ansys Fluent; RANS and uRANS; $k-\epsilon$ and $k-\omega$ turbulence models; EBU, PPDF, and FGM combustion models; Python; Linux}
	\resumeItemListEnd
	
	\resumeSubheading
	{\href{https://www.mae.ncsu.edu/research/facilities-and-labs/}{North Carolina State University}}{Raleigh, NC, USA}
	{Graduate Research Assistant, Computational Combustion and Energy Sciences Lab}{Jan 2012 -- Jul 2012}
	\resumeItemListStart
	\resumeItem{Numerical Simulation and Analysis of Reacting Flows}
	{Used the \href{http://pencil-code.nordita.org/}{Pencil Code}, an open-source MPI code written in Fortran, for Direct Numerical Simulation (DNS) of auto-ignition in hydrogen-air mixtures to study the effects of turbulence intensities and length-scales on flame characteristics as a part of Master's \href{https://repository.lib.ncsu.edu/handle/1840.16/8193/}{thesis} research.}
	\resumeItemListEnd	
	\resumeSubHeadingListEnd
	
	%-----------PROJECTS-----------------
	\section{Academic Projects}
	\resumeSubHeadingListStart
	\resumeSubItem{Development of CFD codes on MATLAB}
	{Generated finite-volume solutions for Poisson\textquoteright s and Navier-Stokes equations with rectangular and curvilinear meshes.}
	\resumeSubItem{Numerical Modeling of Slow Axonal Transport using COMSOL Multiphysics}
	{Solution of the
governing equations of transport of cytoskeletal elements in axons by numerical integration
on Comsol package to understand the dependence of their time evolution on various model parameters.}
	\resumeSubItem{An Experimental Study of Drilling on HCHCR-D2 Steel (\textit{B.E. Project})}
	{Compared conventional drilling and helical milling approaches on a CNC and studied the effects of tool type and vibration on surface finish and tool wear.}
	%\resumeSubItem{An Experimental Study of Drilling on HCHCR-D2 Steel (B.E Project)}
    %{Compared drilling and helical milling for a hard material (56 HRC) on a CNC Machining Center to study the effects of tool type and vibration on surface finish and tool wear.}
	%\resumeSubItem{Digit Recognition}
	%{Used multiclass SVM, softmax regression, and deep learning (FCN, CNN) to recognize digits.}
	%\resumeSubItem{Automatic Review Analyzer}
	%{Used Perceptron and Pegasos algorithms for sentiment analysis of Amazon reviews.}
	%\resumeSubItem{Netflix Movie Ratings}
	%{Used Gaussian mixture models for collaborative filtering to predict movie ratings.}
	%\resumeSubItem{Reinforcement Learning}
	%{Taught an agent to play a simple game using parameterized Q-learning.}
	%\resumeSubItem{Predicting Office Space Prices}
	%{Multivariate polynomial regression from scratch in Python for predictions.}
	\resumeSubHeadingListEnd
	
	%-----------SKILLS-----------------
	\section{Technical Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{CFD Codes}
	{Star-CCM+, Ansys Fluent, OpenFOAM, code\_saturne}
	\resumeSubItem{CAD Packages}
	{SolidWorks, FreeCAD, Salome, Ansys DesignModeler}
	\resumeSubItem{Programming and Scripting Languages}
	{Python, Matlab/GNU Octave, C, Fortran, Shell}
	%\resumeSubItem{Numerical and Plotting Packages}
	%{NumPy, Pandas, SciPy, Matplotlib, Scikit-learn, PyTorch, ggplot}
	%\resumeSubItem{Operating Systems}
    %{GNU/Linux, Windows}
	\resumeSubItem{High Performance Computing}
	{Used AWS and company/university clusters to perform large parallel computations}
	\resumeSubItem{Relevant Graduate Coursework}
	{CFD, Combustion, Turbulent Flows, Thermodynamics, Convective Heat Transfer, Compressible Flows, Acoustic Radiation}
	\resumeSubHeadingListEnd
	
\end{document}